---
title: "Pokemon API R Wrapper"
author: "Connor Lee and Eva Nguyen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package provides an R wrapper for the Pokemon API.   

* Provides a data frame of pokemons from Generation 1 and functions to transform the data frame 
* More information on the API documentation can be found at the official website: [Poke API](https://pokeapi.co/)

## Installation 
Developer GitHub Version
```
library(devtools)   
devtools::install_github("nguyeneva/data534_project/pokeWrapper")
```
**Attention**  
The `devtools` package will need to be installed.

## Loading  <font size="3">pokeWrapper</font> Library
```
library(pokeWrapper)
```

## <font size="3">pokeframe</font> Data Frame
Loading data into console
```
pokeframe
```
```{r, eval=TRUE, include=FALSE}
library(devtools)
devtools::install_github("nguyeneva/playground_/pokeWrapper")
library(pokeWrapper)
```
**Sample Output**   
```{r}
head(pokeframe)
```


## Filtering Data Frame <font size="3">poke.filter</font>

